Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-14 manuscript/manuscript.tex
Beginning of discussion section
Continuation of discussion

>>>>

Currently, this study is limited as we are set within the bounds of this data set. In future studies we can include more predictors in order to see if there are any other factors that could be used to predict diabetes. As well as having an even larger data set in order to ensure our accuracy. Other data sets may suggest that certain predictors are not helpful in predicting diabetes that our model did not pick up on due to the metrics of our data.

As this is a paper dealing with sensitive medical data, we have many limitations in order to be ethical as well as respecting patient privacy. Based on the data set collected we should be able to ensure patient privacy pretty well as names or any very unique identifiers are not listed with each entry. We simply have a ID and age for each entry so we do not have to worry as much for the sake of privacy. In terms of our direct models we may have to disregard some assumptions as they may not fit with real world data. If something unexpected happens we may have to reconsider the data set used and consider finding a new one. This will be done by a case by case scenario and will be investigated thoroughly before making any decisions.
